Introduction to Analysis \\ Assignment 6

### 2017-10-31 Graduate - Introduction to Analysis I/Assignment 6/assignment.tex
update
complete

\problem{10}{Problem 27, Section 18.3, Page}
\solution{Solution}{
a
}
\end{document}

>>>>

\problem{10}{Problem 27, Section 18.3, Page}
\solution{(i)}{
First we show that if $f$ is integrable on $X$, then the set
$$
F = \{x\mid f(x) \ne 0\}
$$
is countable. Otherwise, since $f$ is integrable, it means $f^+ $ and $f^- $ are both integrable. We now assume $f$ is nonnegative, then
$$
F = \bigcup_{n = 1}^{\infty}\{x\mid f(x) \ge \frac{1}{n}\}.
$$
If $F$ is uncountable, then there must exist $n$, s.t. $F_n = \{x\mid f(x) \ge \frac{1}{n}\}$ is uncountable, and $m(F_n) = \infty$. Thus 
$$
\int_{X}fd\eta \ge \int_{F_n}fd\eta \ge \frac{1}{n}\times\infty = \infty,
$$
which makes a contradiction. In this case, suppose there is a bijection from $F$ to a subset of $\mathbb{N}$, then this problem is the same with Problem 8.
}
\solution{(ii)}{
Since $x_0\in X$, and $\mathcal{M}$ is the $\sigma-$algebra of all subsets of $X$, then $\{x_0\}$ is measurable. For any simple function $h(x) \le |f(x)|$, suppose
$$
h(x) = \sum_{i=1}^{n}c_i1_{E_i},
$$
and $x_0 \in c_1$, then 
$$
\int_{X}h(x)d\mu_{x_0} = \sum_{i=1}^{n}c_im(E_i) = c_1 \le |f(x_0)|.
$$
Then according to the definition of integration, 
$$
\int_{X}|f(x)| \le |f(x_0)|.
$$
On the other hand, let
$$
h(x) = \left\{
\begin{aligned}
&|f(x_0)|, ~x = x_0 \\
&0, ~x\ne x_0
\end{aligned}
\right.
$$
then 
$$
\int_{X}h(x) = \int_{\{x_0\}}h(x_0) = |f(x_0)|.
$$
Hence
$$
\int_{X}|f(x)|d\mu_{x_0} = |f(x_0)|.
$$
When $f$ is arbitrary real-valued function, define $f^+ $ and $f^- $ as in the textbook, then $f = f^+-f^- $, and
$$
\int_{X}f = \int_{X}f^+ -\int_{X}f^-.
$$
}
\end{document}
